\thetitle

### 2013-04-18 tfpie/tfpie.tex
Citation for image library.
start on conclusion

  \item the ``World'' approach to developing interactive animations
    and games using functional
    programming~\cite{dvanhorn:Felleisen2009Functional}.
\end{itemize}

@@

>>>>

  \item the ``World'' approach to developing interactive animations
    and games using functional programming and functional
    graphics~\cite{dvanhorn:Felleisen2009Functional,
      local:barland-sfp10}.
\end{itemize}

@@

We have now completed the third iteration of this course, teaching
approximately 35 students each time.  Our experience has been
uniformly positive, and the students have gone on to significant
success in the subsequent courses, despite the curriculum differing
from what the bulk of Northeastern University computer science majors
take.
